Dissertation

### 2012-10-25 dissertation/introsota.tex
SPLENDID and langcase
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@405 43ef1190-90fd-4dd7-a769-d0121f02b80e

@@

All methods used above is based on directed \emph{acyclic} graphs, but
an RDF graph may be cyclic, which may present significant
difficulties. \cite{Lin:2011:LRB:2063016.2063042} addresses this
problem by constraining themselves to an ``Attribute Graph'', which
they define to match a Basic Graph Pattern such as
\begin{verbatim}
x     p1 ?v1 .
?v1   p2 ?v2 .
...
?vn-1 pn ?vn .
\end{verbatim}
(for the formal definition, see
\cite{Lin:2011:LRB:2063016.2063042}). The resulting graph is a
directed acyclic graph.

>>>>

We note that SPLENDID would not solve the \langcase, but since there
were so few languages, there would be other objects that had a lot
more distinct values. They would would be joined earlier in this
specific case and we would be unlikely to see the worst-case
behavior. However, this would be brittle and we seek a better
solution.

@@

All methods used above is based on directed \emph{acyclic} graphs, but
an RDF graph may be cyclic, which may present significant
difficulties. \cite{Lin:2011:LRB:2063016.2063042} addresses this
problem by constraining themselves to an ``Attribute Graph'', which
they define to match a Basic Graph Pattern such as
\begin{verbatim}
x     p1 ?v1 .
?v1   p2 ?v2 .
...
?vn-1 pn ?vn .
\end{verbatim}
(for the formal definition, see
\cite{Lin:2011:LRB:2063016.2063042}). This makes an Attribute Graph a
Directed Acyclic Graph (DAG).
